Max N and S

### 2019-10-31 analysis/reports/statevars.Rmd
try this

loadd(statevars, cache = cache)

@@

statevars_plot <- ggplot(data = statevars, aes(x = s0, y = n0, color = singletons)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_d(end = .5)

@@

statevars_plot_facetted <- statevars_plot +
  facet_wrap(vars(dat))

>>>>

loadd(all_sv, cache = cache)

@@

statevars_plot <- ggplot(data = all_sv, aes(x = s0, y = n0, color = singletons)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_d(end = .5) +
  geom_vline(xintercept = 62) +
  geom_hline(yintercept = 15000)

@@

statevars_plot_facetted <- statevars_plot +
  facet_wrap(vars(dat), scales = "free")
